A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-26 manuscript.Rmd
add section on docker

@@

A considerable number of external dependencies may hinder collaboration and long term reproducibility, but automated solutions can "bundle" and fix dependencies.

>>>>

```
---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
repro:
  scripts:
    - R/simulation.R
---
```

@@

Modern data analysis is only feasible because we rely on much external software.
One downside is that a considerable number of external dependencies may hinder collaboration and long term reproducibility.
The key problem is the fragility of a software setup.
Many components have to fit perfectly together and each change e.g. an update, risks that balance.
Updates are, of course, very much necessary.
Another problem is that the software environment is also variable and what works on one machine, might not work on any other.
Docker circumvents such issues.
Instead of delivering instructions on how to recreate some required components of an analysis, Docker delivers all software that was used in an analysis, down to the operating system.
Docker does this without interfering with the already installed software by using a virtual software environment that is independent of the host software environment.
Such snapshot of the software stack is called "image".
Of course packaging all needed software in such image, requires considerable amounts of storage.
However, two strategies help to keep the storage requirements manageable.
First, there is a community that maintains images for special purposes.
For example, using R [rocker-citation].
Such images only contain what is absolutely necessary for the specific purpose.
Users can then install whatever they additionally need on top of these purpose built images.
The image that was used for this article uses `r round(as.numeric(fs::file_size("reprotutorial.sif"))/1024^3, 2)`Gb of disc space.
It does include R, RStudio, LaTeX as well as many R packages like the tidyverse (amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` packages.)
Second, instead of saving a binary image of the software, one can also save a textual description of the programmatic steps to install the software in a `Dockerfile`.
Such files are very small (the Dockerfile for this project is `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb big), but they rely on the assumption that all software repositories are available and contain the correct software version.
The `repro`-package lets you specify required packages as part of the metadata of the RMarkdown:

```
---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
repro:
  scripts:
    - R/simulation.R
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
---
```

These packages together with the R version that you currently used are then translated into an `Dockerfile`.
